An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-02-10 EconGrowth.Rnw
Changed labels for covariance tables, spelling out "Covariance" in its entirety.

##############################
# Returns an xtable of covariance information for the specified country.
##
covarianceTable <- function(countryAbbrev){
  data <- loadData(countryAbbrev)
  # Grab only the data we want.
  dataForCovar <- cbind(data$iGDP, data$iCapStk, data$iLabor, data$iQ, data$iX)
  names <- c("$y$", "$k$", "$l$", "$q$", "$x$")
  if (countryAbbrev %in% countryAbbrevsU){
    # Add U data only if we have it.
    dataForCovar <- cbind(dataForCovar, data$iU)
    names <- c("$y$", "$k$", "$l$", "$q$", "$x$", "$u$")
  }
  covarResults <- cor(dataForCovar)
  colnames(covarResults) <- names
  rownames(covarResults) <- names
  covarXtable <- xtable(covarResults, 
                      caption=paste("Covariance table for ", countryAbbrev, "economy."), 
                      label=paste("tab:Covar_", countryAbbrev, sep=""))
                      # digits = c(1, 4,4,4, 2,2,2, 2,2,2),
                      # align = "r|ccc|ccc|ccc") #Sets alignment of the numbers in the columns)
  return(covarXtable)
}
@

@@

Figure \ref{fig:Factors_Lattice_Graph} shows historical data. GDP ($y$), capital stock ($k$), labor ($l$), and the various energy types ($q$, $x$, and $u$) track each other closely. Covariances among these variables are rather high as shown in Tables \ref{tab:Covar_US} through \ref{tab:Covar_ZM}.

@@

<<Covar_Table_US, results='asis'>>=
print(covarianceTable("US"), 
                      caption.placement="top", 
                      sanitize.rownames.function = identity,
                      sanitize.colnames.function = identity,
                      table.placement="H")
@

<<Covar_Table_UK, results='asis'>>=
print(covarianceTable("UK"), 
                      caption.placement="top", 
                      sanitize.rownames.function = identity,
                      sanitize.colnames.function = identity,
                      table.placement="H")
@

<<Covar_Table_JP, results='asis'>>=
print(covarianceTable("JP"), 
                      caption.placement="top", 
                      sanitize.rownames.function = identity,
                      sanitize.colnames.function = identity,
                      table.placement="H")
@

<<Covar_Table_CN, results='asis'>>=
print(covarianceTable("CN"), 
                      caption.placement="top", 
                      sanitize.rownames.function = identity,
                      sanitize.colnames.function = identity,
                      table.placement="H")
@

<<Covar_Table_ZA, results='asis'>>=
print(covarianceTable("ZA"), 
                      caption.placement="top", 
                      sanitize.rownames.function = identity,
                      sanitize.colnames.function = identity,
                      table.placement="H")
@

<<Covar_Table_SA, results='asis'>>=
print(covarianceTable("SA"), 
                      caption.placement="top", 
                      sanitize.rownames.function = identity,
                      sanitize.colnames.function = identity,
                      table.placement="H")
@

<<Covar_Table_IR, results='asis'>>=
print(covarianceTable("IR"), 
                      caption.placement="top", 
                      sanitize.rownames.function = identity,
                      sanitize.colnames.function = identity,
                      table.placement="H")
@

<<Covar_Table_TZ, results='asis'>>=
print(covarianceTable("TZ"), 
                      caption.placement="top", 
                      sanitize.rownames.function = identity,
                      sanitize.colnames.function = identity,
                      table.placement="H")
@

<<Covar_Table_ZM, results='asis'>>=
print(covarianceTable("ZM"), 
                      caption.placement="top", 
                      sanitize.rownames.function = identity,
                      sanitize.colnames.function = identity,
                      table.placement="H")
@

>>>>

##############################
# Returns an xtable of covariance information for the specified country.
##
covarianceTable <- function(countryAbbrev){
  data <- loadData(countryAbbrev)
  # Grab only the data we want.
  dataForCovar <- cbind(data$iGDP, data$iCapStk, data$iLabor, data$iQ, data$iX)
  names <- c("$y$", "$k$", "$l$", "$q$", "$x$")
  if (countryAbbrev %in% countryAbbrevsU){
    # Add U data only if we have it.
    dataForCovar <- cbind(dataForCovar, data$iU)
    names <- c("$y$", "$k$", "$l$", "$q$", "$x$", "$u$")
  }
  covarResults <- cor(dataForCovar)
  colnames(covarResults) <- names
  rownames(covarResults) <- names
  covarXtable <- xtable(covarResults, 
                      caption=paste("Covariance table for ", countryAbbrev, "economy."), 
                      label=paste("tab:Covariance_", countryAbbrev, sep=""))
                      # digits = c(1, 4,4,4, 2,2,2, 2,2,2),
                      # align = "r|ccc|ccc|ccc") #Sets alignment of the numbers in the columns)
  return(covarXtable)
}
@

@@

Figure \ref{fig:Factors_Lattice_Graph} shows historical data. GDP ($y$), capital stock ($k$), labor ($l$), and the various energy types ($q$, $x$, and $u$) track each other closely. Covariances among these variables are rather high as shown in Tables \ref{tab:iance_US} through \ref{tab:Covariance_ZM}.

@@

<<Covariance_Table_US, results='asis'>>=
print(covarianceTable("US"), 
                      caption.placement="top", 
                      sanitize.rownames.function = identity,
                      sanitize.colnames.function = identity,
                      table.placement="H")
@

<<Covariance_Table_UK, results='asis'>>=
print(covarianceTable("UK"), 
                      caption.placement="top", 
                      sanitize.rownames.function = identity,
                      sanitize.colnames.function = identity,
                      table.placement="H")
@

<<Covariance_Table_JP, results='asis'>>=
print(covarianceTable("JP"), 
                      caption.placement="top", 
                      sanitize.rownames.function = identity,
                      sanitize.colnames.function = identity,
                      table.placement="H")
@

<<Covariance_Table_CN, results='asis'>>=
print(covarianceTable("CN"), 
                      caption.placement="top", 
                      sanitize.rownames.function = identity,
                      sanitize.colnames.function = identity,
                      table.placement="H")
@

<<Covariance_Table_ZA, results='asis'>>=
print(covarianceTable("ZA"), 
                      caption.placement="top", 
                      sanitize.rownames.function = identity,
                      sanitize.colnames.function = identity,
                      table.placement="H")
@

<<Covariance_Table_SA, results='asis'>>=
print(covarianceTable("SA"), 
                      caption.placement="top", 
                      sanitize.rownames.function = identity,
                      sanitize.colnames.function = identity,
                      table.placement="H")
@

<<Covariance_Table_IR, results='asis'>>=
print(covarianceTable("IR"), 
                      caption.placement="top", 
                      sanitize.rownames.function = identity,
                      sanitize.colnames.function = identity,
                      table.placement="H")
@

<<Covariance_Table_TZ, results='asis'>>=
print(covarianceTable("TZ"), 
                      caption.placement="top", 
                      sanitize.rownames.function = identity,
                      sanitize.colnames.function = identity,
                      table.placement="H")
@

<<Covariance_Table_ZM, results='asis'>>=
print(covarianceTable("ZM"), 
                      caption.placement="top", 
                      sanitize.rownames.function = identity,
                      sanitize.colnames.function = identity,
                      table.placement="H")
@
